Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
add author name of iptables tutorial

\subsection{More about iptables}
This was just a brief introduction to iptables/netfilter. If you want to know more about iptables configuration, you can have a look at this excelent and detailed tutorial : http://www.frozentux.net/iptables-tutorial/iptables-tutorial.html
\newpage

>>>>

\subsection{More about iptables}
This was just a brief introduction to iptables/netfilter. If you want to know more about iptables configuration, you can have a look at this excellent and detailed tutorial by Oskar Andreasson : \href{http://www.frozentux.net/iptables-tutorial/iptables-tutorial.html}{http://www.frozentux.net/iptables-tutorial/iptables-tutorial.html}
\newpage
